---
title: "House_Prediction"
output: word_document
---

TO DO AND IMPORTANT LINKS:
1. Seperate x_train and y
2. https://stackoverflow.com/questions/16961921/plot-data-in-descending-order-as-appears-in-data-frame
3.https://www.kaggle.com/dgawlik/house-prices-eda 
4.https://cran.r-project.org/web/packages/dlookr/vignettes/transformation.html
5.http://www.sthda.com/english/wiki/visualize-correlation-matrix-using-correlogram
6.https://cran.r-project.org/web/packages/corrplot/vignettes/corrplot-intro.html

```{r}
train=read.csv("C://Users//sherr//Desktop//KAGGLE//train.csv")
test=read.csv("C://Users//sherr//Desktop//KAGGLE//test.csv")
```

```{r}
library(dplyr)
```



```{r}
str(train)
```
```{r}
str(test)

```

# TO CHECK DATA TYPE PROPORTION
```{r}
library(ggplot2)
data_types <- function(frame) {
  res <- lapply(frame, class)
  res_frame <- data.frame(unlist(res))
  
  
 
  print(res_frame)
  
  print(ggplot(data=res_frame,aes(x=unlist.res.))+
    geom_bar( fill="steelblue") +
    xlab("data types")+ggtitle("Plot of datatypes in training data types")+
    geom_text(stat='count', aes(label=..count..),        vjust=1.4,color="white")) 
  
    #geom_text(aes(label=unlist.res.,vjust=1.6,color="white"))
} 


```










# TO CHECK DATATYPE OF TRAIN AND TEST SET

```{r}

library(ggplot2)
data_types <- function(frame,nam) {
  res <- lapply(frame, class)
  res_frame <- data.frame(unlist(res))
  
  
 
  
  
  ggplot(data=res_frame,aes(x=unlist.res.))+
    geom_bar( fill="steelblue") +
    xlab("data types")+ggtitle(paste0(" Plot of datatypes of data types of ",nam))+
    geom_text(stat='count', aes(label=..count..), vjust=1.4,color="white") 
  
    #geom_text(aes(label=unlist.res.,vjust=1.6,color="white"))
} 


```


```{r}
data_types(train,"train")
```
```{r}
data_types(test,"test")
```


# DESCRIPTION OF DATAFRAME

# TO CHECK WHICH VALUES ARE GREATER THAN 0
```{r}
missing_values_check=function(dataframe){
  na_count_miss1 <-sapply(dataframe,function(x) sum(is.na(x)))
  na_count_miss1 <- data.frame(na_count_miss1)
  na_count_miss1=na_count_miss1%>%
    filter(na_count_miss1>0)
  
  na_count2 <- cbind(newColName = rownames(na_count_miss1), na_count_miss1)
  rownames(na_count2) <- 1:nrow(na_count2)
  count_missing <- na_count2[order(-na_count2$na_count),]
  print(count_missing)
  }
#na_count_miss = na_count_miss[order(-na_count_miss$na_count_miss),]
  
```



```{r}
missing_values_check(train)
```

```{r}

library(naniar)
gg_miss_upset(train, order.by = "freq", nsets = 12)
```
This plot represents the descending order of missing values. Pool_QA has highest missing value followed bt MissFeature_NA,AlleyNa etc

Missing Values are more than 200 in 6 columns which are 1/7th of the total values. Hence using them in our analysis would not be useful. However to confirm lets just make a correlation plot for their relative importance





# PERCENTAGE OF MISSING

```{r}
missing_values_percentage_check=function(dataframe){
  na_count_miss1 <-sapply(dataframe,function(x) sum(is.na(x))/1460)
  na_count_miss1 <- data.frame(na_count_miss1)
  na_count_miss1=na_count_miss1%>%
    filter(na_count_miss1>0)
  
  na_count2 <- cbind(newColName = rownames(na_count_miss1), na_count_miss1)
  rownames(na_count2) <- 1:nrow(na_count2)
  count_missing <- na_count2[order(-na_count2$na_count),]
  print(count_missing)
  }
```

```{r}
perc_miss=missing_values_percentage_check(train)
```
One of the most Notable thing our dependent value y does not have missing values





```{r}

#q <- ggplot(perc_miss, aes(x=perc_miss$newColName,y=perc_miss$na_count_miss1))+geom_bar() 
  
q <- ggplot(perc_miss, aes(x=reorder(newColName,-na_count_miss1),y=na_count_miss1),las=2)+geom_col()+
  theme(axis.text.x = element_text(angle = 90))+ggtitle("percentages of missing value")+xlab("Features")+ylab("count")
  #scale_x_discrete(breaks=1:nrow(perc_miss),labels=perc_miss$newColName)
q
```









POOLQC,Missfeature ,Alley,Fence are all greater than 80%

```{r}
train_data= subset(train,select=-c(PoolQC,MiscFeature,Alley,Fence))
print(train_data)

```
```{r}
test_data= subset(test,select=-c(PoolQC,MiscFeature,Alley,Fence))
print(test_data)
```


# MISS FOREST - FILLING MISSING 

```{r}


library(woeBinning) # 'germancredit' data
library(PRROC) # ROC curves in data frames
library(tidyverse) # everything
library(imputeMissings) # median/mode imputation
library(visdat) # missingness plots
library(doParallel) # parallel missForest
library(doRNG) # reproducible parallel results
library(gridExtra) # combining graphs
library(randomForest) # random forests
library(missForest) # ...
library(kableExtra) # pretty tables

options(scipen = 999) # no scientific notation

RNGkind(kind = "Mersenne-Twister", 
        normal.kind = "Inversion", 
        sample.kind = "Rejection") # because different versions of R giving different RNG results annoys me

theme_set(theme_light()) # ggplot theme
```


```{r}

```



AS WE WANT DATA IN FORM OF FACTORS IN TO APPLY MISSFOREST . HENCE WE CHECK IF OUR DATA HAS ANY FACTORS
```{r}
f <- sapply(train_data, is.factor)

which(f)
```

```{r}
library(dplyr)
train_data <- train_data %>% 
  mutate_if(is.character, as.factor)
test_data <- test_data %>% 
  mutate_if(is.character, as.factor)
```

```{r}
imputed_train = missForest(train_data)$ximp

```
```{r}
imputed_test=  missForest(test_data)$ximp
```

```{r}
imputed_train
```
```{r}
gg_miss_upset(imputed_train, order.by = "freq", nsets = 12)

```



```{r}
#gg_miss_upset(imputed_test, order.by = "freq", nsets = 12)
```
hence both shows no missing values


# STANDARDIZATION

# VISUALIZATIONS

```{r}
library("dplyr")                                     # Load dplyr

data_num2 <- select_if(imputed_train, is.numeric)             # Subset numeric columns with dplyr
data_num2

    
```



# STANDARDIZATION  AND VISUALIZATION


```{r}
ggplot(data_num2, aes(x=data_num2[,"SalePrice"]))+
    geom_histogram(aes(y=..density..),      # Histogram with density instead of count on y-axis
                   binwidth=.5,
                   colour="black", fill="white") +geom_density(alpha=.2, fill="#FF6666")+
              ggtitle(paste0(" Plot of distribution of response variable ",colnames(data_num2)[i]))+xlab("values")
```

There is Skewness in response variable Sales Prices 

```{r}
for (i in 1:length(data_num2)){
    print(ggplot(data_num2, aes(x=data_num2[,i]))+
    geom_histogram(aes(y=..density..),      # Histogram with density instead of count on y-axis
                   binwidth=.5,
                   colour="black", fill="white") +
    geom_density(alpha=.2, fill="#FF6666")+ggtitle(paste0(" Plot of distribution of ",colnames(data_num2)[i]))+xlab("values"))
  }
  
```

All our explanatory variables are not normally distributed. 



# CORRELATION PLOT

```{r}

library(corrplot)
corrplot(cor(data_num2), method="color",tl.cex = 0.5)
# tl.cex helped change the size of axis labels
```


```{r}
library(dplyr)

correl=corr_dat %>%
  select("SalePrice")
```



```{r}
library(formattable)
corr_data2=formattable(corr_dat, list(
  SalePrice = formatter("span", 
                         style = ~style(font.weight = "bold", color = 
                                          ifelse(SalePrice > 0.5,"red",
                                                 ifelse(SalePrice< -0.5,"green",NA
                                                        ))))))
corr_data2
```

```{r}
library(formattable)
formattable(correl, list(
  SalePrice = formatter("span", 
                         style = ~style(font.weight = "bold", color = 
                                          ifelse(SalePrice > 0.5,"red",
                                                 ifelse(SalePrice< -0.5,"green",NA
                                                        ))))))

```

